{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-31 paper/tex/sections/appendix.tex
minor changes to variations
add 10yr nums to table (only missing 2 sims now)

\subsection{Detection rate table}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type. Each value shows the mean and the 1-$\sigma$ Poisson uncertainty. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \begin{tabular}{cl|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{3}{c|}{LISA detections (4 year)} & \multicolumn{3}{c}{LISA detections (10 year)} \\ \cline{3-8}
        & & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & Fiducial & \confinv{73.7}{8.7}{8.3} & \confinv{42.1}{6.1}{6.9} & \confinv{7.9}{2.9}{3.1}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.6}{8.6}{8.4} & \confinv{22.3}{4.3}{4.7} & \confinv{2.9}{1.9}{2.1}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{46.8}{6.8}{7.2} & \confinv{8.2}{3.2}{2.8} & \confinv{3.9}{1.9}{2.1}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.8}{6.8}{7.2} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3}\\
        E & Case BB mass transfer is always unstable & \confinv{69.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{0.2}{0.2}{0.8}\\
        F & Model E + Model K & \confinv{153.8}{12.8}{12.2} & \confinv{147.8}{11.8}{12.2} & \confinv{18.2}{4.2}{3.8}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{27.8}{4.8}{5.2} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{61.7}{7.7}{8.3} & \confinv{28.1}{5.1}{4.9} & \confinv{6.2}{2.2}{2.8}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{71.6}{8.6}{8.4} & \confinv{38.1}{6.1}{5.9} & \confinv{31.1}{5.1}{5.9}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
        K & HG donor stars initiating a CE survive CE & \confinv{154.1}{12.1}{12.9} & \confinv{58.9}{7.9}{8.1} & \confinv{9.6}{2.6}{3.4}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{50.2}{7.2}{6.8} & \confinv{70.0}{8.0}{8.0} & \confinv{6.6}{2.6}{2.4}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{95.9}{9.9}{10.1} & \confinv{30.0}{5.0}{5.0} & \confinv{7.1}{3.1}{2.9}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.1}{8.1}{7.9} & \confinv{51.7}{6.7}{7.3} & \confinv{8.2}{3.2}{2.8}\\
        O & PISN and pulsational-PISN not implemented & \confinv{75.1}{9.1}{8.9} & \confinv{43.2}{6.2}{6.8} & \confinv{7.9}{2.9}{3.1}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.4}{9.4}{8.6} & \confinv{86.3}{9.3}{9.7} & \confinv{15.4}{4.4}{3.6}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.5}{9.5}{9.5} & \confinv{142.4}{12.4}{11.6} & \confinv{33.4}{5.4}{5.6}\\
        R & Black holes receive not natal kick & \confinv{85.9}{8.9}{9.1} & \confinv{95.8}{9.8}{10.2} & \confinv{9.7}{2.7}{3.3}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.4}{8.4}{8.6} & \confinv{33.9}{5.9}{6.1} & \confinv{8.8}{2.8}{3.2}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{14.9}{3.9}{4.1} & \confinv{9.6}{3.6}{3.4}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

@@

\subsection{Detection rates relative to fiducial model}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs. The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

>>>>

\subsection{Detection rate table}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type. Each value shows the mean and the 1-$\sigma$ Poisson uncertainty. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \begin{tabular}{cl|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{3}{c|}{LISA detections (4 year)} & \multicolumn{3}{c}{LISA detections (10 year)} \\ \cline{3-8}
        & & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & Fiducial & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{47.0}{7.0}{7.0} & \confinv{8.3}{3.3}{2.7} & \confinv{3.9}{1.9}{2.1} & \confinv{75.8}{8.8}{9.2} & \confinv{13.6}{3.6}{3.4} & \confinv{6.4}{2.4}{2.6}\\
        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
        E & Case BB mass transfer is always unstable & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \confinv{0.2}{0.2}{0.8} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \confinv{0.4}{0.4}{0.6}\\
        F & Model E + Model K & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \confinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
        G & CE efficiency $\alpha = 0.1$ & \confinv{27.9}{4.9}{5.1} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{43.9}{6.9}{7.1} & \confinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
        H & CE efficiency $\alpha = 0.5$ & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
        I & CE efficiency $\alpha = 2.0$ & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
        J & CE efficiency $\alpha = 10.0$ & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \confinv{34.9}{5.9}{6.1} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \confinv{57.2}{7.2}{7.8}\\
        K & HG donor stars initiating a CE survive CE & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
        L & Fryer rapid SN remnant mass prescription & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
        O & PISN and pulsational-PISN not implemented & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.7}{8.7}{9.3} & \confinv{86.6}{9.6}{9.4} & \confinv{15.4}{4.4}{3.6} & \confinv{130.1}{11.1}{11.9} & \confinv{145.1}{12.1}{11.9} & \confinv{25.6}{4.6}{5.4}\\
        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
        R & Black holes receive not natal kick & \confinv{133.8}{11.8}{11.2} & \confinv{159.6}{12.6}{12.4} & \confinv{16.0}{4.0}{4.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{25.3}{5.3}{4.7} & \confinv{15.6}{3.6}{4.4} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

@@

\subsection{Detection rates relative to fiducial model}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs. The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:dco_relative_rates}
\end{figure*}
